\chapter{The Job}

% 14th October until 16th October

\paragraph{August 31, 9:40; Fuzzy HQ}
I am standing.
The train leaves in an hour.
Planning seems to have gifted me too much of a temporal buffer zone.
I wait.

This is going to be a low profile job.
Besides me, there is only agent Bubble joining the cause.

We are ready, The handbook is with her.
I do leave the toilet paper behind this time.
I will.
Seriously.
Modern plumbing \emph{will} prevail.
Wherever we go.
I believe.

If anything goes wrong, we have the training to cope.
\emph{There is no need for alarm.}

\paragraph{August 31, 13:45; Gate 38B}
Deja vu, I suspect I have departed from this gate before.
Conspiracy.
Agent Bubble suspects this as well.
Nevertheless we shall board the flight in a couple of minutes.

We will change flights below sea level: In Amsterdam.
If global warming speeds up significantly in the next few hours, the mission will be in jeopardy.

\paragraph{August 31, 14:30; In the Air}
Agent Bubble proposed a struggle for galactic dominance.
Humans against Hydraxians.
Wish me luck.

\paragraph{August 31, 16:15; Amsterdam Airport}
No conclusion on galactic domination.
Had to hurry through half of the airport.
We passed bricks of dessert.
Checked through security checks.
Passed through passport control.
Figured out the sub gate the bus departs from.
Got herded into the last bus going out to the airfield.

As I write this, we are winding down from the hurry.
The security instructions are being given.
In Dutch.
"`Damenen und Herrenen\ldots{}"'

Agent Bubble is writing the backup logfile.
It should confuse anyone trying to triangulate actual events from any of the reports.

And across the sea we gooo\ldots

\paragraph{August 31, 21:25; Holiday Inn Express Waterfront, Room 344}
The prepared bus schedules seem to work as guidelines only, not actual rules.
Yet we nailed the stop in front of the hotel on the first attempt.
Bed!
Shower!
Sleep!

Intelligence wise, there was a lot of very old architecture on the way from the Airport (Line 100 Airlink Express) to Waverley Station and onward to the Ocean Front (Line 22).
Had burgers for Dinner.
\emph{Coleslaw-NOM!}
Now shower and sleep - so tired.

\paragraph{September 1, 15:30; Edinburgh Castle}
We are on tour.
It is fiendishly cold outside and the wind threatens to blow our hats away.
It already came close once.

We wandered through some exhibitions and then ended up staring at Scottish Crown Jewels.
They had been lost to the sock drawer for a century before being rediscovered.
Well\ldots not exactly "`sock drawer"', like like "`big wooden box walled up in a room inside a big castle"', but that is where I keep \emph{my} socks.
So, not much of a difference, right?

We also wandered through tons of tourists in an old POW prison.
Agent Bubble did not appreciate the dark and narrow interior, she is more at home with bright and crowded.

Now we had some tea, except me which had ginger beer.
And a scone.
Delicious.

\paragraph{September 1; Room 344}
We left the big cannon at Edinburgh castle and jumped the tour bus back to Waverly, listening to kid's stories on the way.
Agent Bubble managed to fall asleep on the trip.

We stocked up on supplies for tomorrow's operation locating a Indian/Nepalese double-agent specializing in food provisioning for dinner.
Language barriers aside, much yams were had.

Our keen perception had found that there was something afoot in Town during the day.
Big stages being set up, streets becoming closed for traffic\ldots
We deducted a concerted firework was going to start, so we snuck in between the civilians and waited for the 9 p.m. starting signal.

It came 45 minutes after we took position.
We were frozenly impressed by the fireworks we witnessed burning down some of the shrubbery around the castle.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Castle under Fire"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Watch Edinburgh Castle Fireworks burn down the shrubbery} \\
\end{tabular}
\end{center}

\paragraph{September 2; Train to Dalmeny}
Major transportation reschedule.
Inability to locate bus stop resulted in going to South Queensferry via Waverly.

Agent Bubble seems much more useful than myself when locating train connections.
Note to self: \emph{Shut up and follow.}

\paragraph{September 2, 20:40; Room 443}
We had a Fried Mars Bar.
Why this was, nobody knows.
It was sweet and sticky.
Very sticky.
\emph{Horribly} sticky.
Never doing that again.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Burn Mars!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Have a Fried Mars Bar} \\
\end{tabular}
\end{center}

Dinner was more on the Scottish side with meat and haggis.
Tastes like leberwurst.

Oh and yes, we were on a ship.
With waves and such things.
Sailed around the Firth of Forth with a stop on Inchcolm Island.
It is pretty marooned with a scenic ruin of an abbey.
Now ruled by Seagulls.
The whole island is littered with dead gulls, feathers and bird droppings.

Strong winds threatened to dehat the both of us.
We stood vigilant.
Still not missing the toilet paper, should have brought a lavatory though.
Inchcolm island was missing an implement to properly wash hands.
And insect/seagull repellant.

\paragraph{September 3, 21:30; Dalhousie Castle}
We shopped for Moon Cakes and "`what-the-hell-is-that-symbol"' roots in chinese supermarkets.
Then we set out for Dalhousie, which seems to be quite far out in the countryside.
We missed the bus stop we were supposed to get out because it was named nothing like the bus stops on any map.
Then we walked along the main road to the badly signed out castle.

\paragraph{September 4, 23:10; Strathallam Guest House R°1}
Back from the Ghost Walk.
T'was not as scary as I'd hoped, too much "`suspense-low voice-scream"' kind of stories and not enough psychological warfare for my taste.
Solidly executed nonetheless.

Previously I was interrupted when logging out yesterday's events, so here's a recap.

The castle turned up between a field and a forest, next to some tethered birds of prey.
By the looks of it a wedding was in full progress and we would have to deal with the fallout later in the evening.
For now we checked in and got to carry our baggage up three flights of stairs.
Through a plethora of doors into a disappointingly plain room number 16.
"`Themed"' in the context of this castle seems to refer to nailing a few unmotivated drapes to the windows.
We were not impressed.
So off to the spa we went.
This was also a bit less than expected, but I made up for this by losing my keys in the bubbling pool.
We spent half an hour fishing them back out, soaking a bath shoe and a bathrobe belt and excavating a prehistoric piece of wood from the pool in the process.
Afterwards we enjoyed the small steam bath and relaxation room until dinner.

This started in the library where the waiter's accent occasionally confused the hell out of us.
Then the proceedings went down to the dungeon where Agent Bubble did a perfect impression of my face when I checked in at a Riocan in Japan:
Being totally bewildered of too much service.
It was surprising to learn we had to eat the food ourselves after all.
Then the fallout in form of bag pipes accompanying the wedding guests entering the vault arrived.

All in all: Food gread, spa okay, room disappointing.

Remember, to get into Strathallam Guest House: 6678.
Since we had not announced our arrival (both agents neglected to follow the instructions on the booking), the entrance code to the premises had to be described to us by phone.

\paragraph{September 5, 17:15; Strathallam R°1}
After a hearty 8:15 breakfast, we hopped the bus to Pencaitland, promptly misordering the ticket.
I suspect the bus driver did not quite get what we wanted.
The drive took about an hour before we hopped off.
So another struggle for galactic domination was started.
Hydraxians versus Mechanar, but it did not finish in time.
During the walk to the distillery (our target for the day) we befriended a german infiltress named Lisa.
We were unable to determine her goals but no hostilities ensued, so we went about our business.
The walk was about 30 minutes on paved roads through farmland framed by hedges.

The distillery tour was quite fragrant, the smell of wort reminds of soy sauce.

The "`Flavor of Scotland"' tour ended with tasting of a lot of whiskeys.

We went for Singletin, Lagavulin and others.
Finally some solid intelligence!
We brought back two bottles.

Now preparing for the rest of the evening.
Wireless I-Net seems to be notworking.

\paragraph{September 6, 20:00; Train to Edinburgh}
We had our excursion to Glasgow today.
Obviously it is a hot spot for soccer enthusiasts as fun crowds sweep around the streets.
Other than that there is a distinct lack of castle offset by an abundance of other architecture.
We vistited an art gallery (modern) and a house (oldest).
Then went through St. Mungo's Cathedral featuring stuff from religions from all over the world.

We eventually ended up in the Glasgow Necropolis, a huge old graveyard on a hill where gravestones litter the paths.
Spooky but impressive.

We rounded the day off by having the worst Italian dinner ever.
I suspect the cook burnt my penne.
Maybe the Scots are on to us, sabotaging our mission with bad food.

\paragraph{September 6, 21:15; Strathallam R°1}
It is raining.
We took a beeline back to the guest house and prepared sammiches.

PS: Our Italian does not hold up, both of us struggled with the difference between "`Signori"' and "`Signore"'.

Tour de Lock follows tomorrow.

\paragraph{September 7, 13:30; Aboard the Sir Walter Scott}
The breakfast was handled at break-neck speed and we already burnt through the sandwiches.
The weather keeps on the brink of the acceptable, the torrents could come down at any time though.
The tour started okay, there is some bumpy driving but the scenery is nice.

The guy driving the tour is a seasoned ex-government worker with a few stories about Scotland on him.

He also sings along to the Scottish folk songs he puts on in the bus.
I also suspect he was a radio host once.

Currently we're stuck on the Sir Walter Scott cruising around Loch Katrine.
It is quite windy and the chill goes to the bone after a while.
As a countermeasure, they have a bar serving hot chocolate.
I had mine with a shot of Brandy.
Delicious.

There is quite a lot of Highlands to see.
Agent Bubble quite likes the hillside.
Also we were promised Highland Cows in the afternoon.

\paragraph{September 7, 21:45; Strathallam R°1}
Stirling Castle was a fun visit, mainly because of the excellent tour guide.
Castle itself looks quite impressive since they poured a boatload of money into reconstructing the building and the furniture.

There was also some more background on the king/queen stuff that they had going on in the middle ages.
I think I slowly get an idea how the political hubbub fits together.
And some of the king's strategy talents were quite facepalm-worthy.

Had dinner at a pub.
Dessert was pudding.
Agent Bubble strongly disagrees with the local definition of pudding.
As it was less creamy and more doughy.
Ar least it was 100\% sticky and stuffy.

Unfortunately we failed to locate any eatery that would serve clooty dumplings.
As a compensation we bagged some canned haggis and cock-a-leekie, missed a bus because Agent Bubble wanted to buy books and I acquired Scarves.

Homecoming was delayed because a Taxi broke down in the middle of the street.

\paragraph{September 8, 20:20; Strathallam R°1}
We've been Closerunning, starting at the top of the Royal Mile and working our way down, trailing off into the side alleys where possible.
Some are closed off to the public (how very upper class) others are just not presentable and give the whole back alley thing a bad name.
Some are quite charming, disclosing a hidden garden, a seduced tavern or a long forgotten shrubbery.
At 10:15 we interrupted for a visit to Mary King's Close.
Impressive, fun and underground.
We had a guide telling a lot about hygiene, the plague and thunder boxes down in a close that had been covered up to build more Edinburgh on top.
'Twas a bit musty and a bit tight but quite interesting.
After making a fool of ourselves to the infrared camera, we were let out.

Lunch was in one of the aforementioned hidden taverns.
Afterwards we went inspecting Holyrood Palace.
It is somewhat very\ldots{} medieval\ldots{} to find out intimate affairs of state were discussed in the king's bedroom.
Other than that there were mostly big rooms built to impress, with very old furniture.

From there we strolled out of the garden (a bit boring because it was mostly lawn and "`do not leave marked paths"'-signs) and up Arthur's Seat (which was a bit windy but quite scenic) where we had a nice overview of the whole of Edinburgh.
And of dogs.
And kids.
And messages written with pebbles.
And dogs.

Also, we could see our other hotel from here.

We decided to add another hill to our list and hiked up Carton Hill.

Monument beside monument we were able to witness a government building project which was supposed to replicate the Acropolis in Athens, but they got only up to a dozen columns before they ran out of money.
We also completed out our main objective at that point.
The picture remains classified though.

After Agent Bubble almost (she claims not at all) fell asleep, we headed back for the day.

There was still no need for the toilet paper, but my pen seems to be running out of ink.

\paragraph{September 9, 20:30; Strathallam R°1}
Sweet endings.
'tis the final day of the stay.
Tomorrow we head back, so we completed a few of the things we previously missed.
We scaled the Scott Monument.
It is very high, with many steps on increasingly narrow spiral staircases.
You can see the city from up there.
Well\ldots{} it stands in the middle of it.
Anyways, we scaled the monument and got a huge ticket for it.
We also saw squirrels from up there (during the day to follow we got to see half a dozen of them.)
Afterward we headed for fudge and then got us some pie, exploring the rest of the New Town and the adjacent gardens (which are closed to the general public unless you arrange key with the city clerk. Elitist Bastard.)
And finally we ended up at the National Scottish Museum once again and got to the industrial age of Scotland before they closed again.
Quickly investigating the Cybraphone (?) before leaving.
Dinner followed with a mighty Cranachan dessert.
Now we are preparing to leave.
\emph{Bagpipes playing}

\paragraph{September 9, 23:05; Room°1}
Agent Bubble convinced me to go out and join a Pub Quiz.
We lost horribly but it was good fun.
Also I do not seem to be able to write down good jokes when tipsy.


